{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-04-24 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

            % ==========================================

@@

                    \mathbb E(L_f, \kappa_f, X) &\subseteq \mathbb F(L_f, \kappa^2/L_f, X), 

@@

                Denote $\bar x^+_\Pi = \Pi_{X^+}x^+$. 
                Using \eqref{ineq:proj-grad} with $z = \bar x^+_\Pi$ it yields: 

@@

                    \right)^2

@@

                Using property of projection onto $X$ we have 
                    \Vert x - \bar x\Vert &\le \Vert x - x_\Pi^+\Vert

@@

                    \Vert x^+ - x^+_\Pi\Vert. 

@@

            Let $\bar v = (\bar y, \bar x_1, \bar x_2, \xi) \in \RR^m\times \RR^{n_1} \times \RR^{n_2}\times \RR$ then the right multiplication of has: 
            \begin{align*}
                \bar v^TA  &= (
                    E_1^T\bar y + \xi c_1^T,\; E_2^T\bar y + \xi c_2^T,\; 
                    \bar x_1^TE_1^T + \bar x_2^TE_2^T - \xi b^T,\; \bar x_1^T
                )
                \\
                &= 
                (
                    E_1^T\bar y + \xi c_1, \;
                    E_2^T \bar y + \xi c_2, \;
                    E_1\bar x_1 + E_2\bar x_2 - \xi b, \;
                    \bar x_1
                )^T. 
            \end{align*}
            \begin{enumerate}
                \item Two multiplications of $E$: $\bar y$ on the left and for $\bar x_1, \bar x_2$ on the right, 
                \item one vector addition with $c = (c_1, c_2)$ and $b$. 
            \end{enumerate}
            Therefore, computing $A^TAv$ has four vector multiplications using $E$. 
            In practice, a sparse matrix $E$ from the model can speed up computations. 
            \par
            Another key operation would be $A^TAv$. 
            Let $\bar v = Av$, then 
            \begin{align*}
                A^TAv &= 
                \begin{bmatrix}
                    E^T_1(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_1
                    \\
                    E^T_2(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_2
                    \\
                    E_1(E_1^Ty + z) + E_2E_2^Ty - (c_1^Tx_1 + c_2^Tx_2 - b^Ty)b
                    \\
                    E_1^Ty + z
                \end{bmatrix}
                \\
                &= 
                \begin{bmatrix}
                    (E_1^TE_1 + c_1^T)x_1 + (E_1^TE_2 + c_2^T)x_2 - (c_1b^T)y
                    \\
                    (E_2^TE_1 + c_1^T)x_1 + (E_2^TE_2 + c_2^T)x_2 - (c_2b^T)y
                    \\
                    -(bc_1^T)x_1 - (bc_2^T)x_2 + (E_2E_2^T + E_1E_1^T + bb^T)y
                    + (E_1E_1^T)z
                    \\
                    E_1^Ty + z
                \end{bmatrix}. 
            \end{align*}
            In practice, implicitly representing the process of $A^TAv$ is better in computing software. 
            Here we write it out to view, for theoretical interests. 
            \par
            Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
            Its gradient, objective value, and Bregman Divergence have: 
            \begin{align*}
                \nabla f(v) &= A^TAv - A^Td, 
                \\
                f(v) &= 
                \frac{1}{2}\langle x, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
                \\
                D_f(x, y) &= \langle x - y, A^TA (x - y)\rangle
                \\
                &= \langle \nabla f(x) - \nabla f(y), x - y\rangle. 
            \end{align*}
            The value $\nabla f(v), f(v)$ when evaluated together, require minimal additional computations. 
            This fact is favorable for implementations in practice.

@@

@@

                \frac{L}{2}\Vert x^+ - x_{-1}\Vert^2. 

@@

@@

@@

@@

@@

    \section{Practical enhencements}

>>>>

            % ==========================================================================================================

@@

                    \mathbb E(L_f, \kappa_f, X) &\subseteq \mathbb F(L_f, \kappa^2_f/L_f, X), 

@@

                Denote $x^+_\Pi = \Pi_{X^+}x^+$. 
                Using \eqref{ineq:proj-grad} with $z = x^+_\Pi$ it yields: 

@@

                    \right)^2.

@@

                Let $x_\Pi = \Pi_{X^+}x$, using the property of projection onto $X$ we have 
                    \Vert x - x_\Pi\Vert &\le \Vert x - x_\Pi^+\Vert

@@

                    \Vert x^+ - x^+_\Pi\Vert &\ge
                    \Vert x - x_\Pi\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert. 

@@

            Let $\bar v = (\bar y, \bar x_1, \bar x_2, \xi) \in \RR^m\times \RR^{n_1} \times \RR^{n_2}\times \RR$ then the right multiplication of has: 
            \begin{align*}
                \bar v^TA  &= (
                    E_1^T\bar y + \xi c_1^T,\; E_2^T\bar y + \xi c_2^T,\; 
                    \bar x_1^TE_1^T + \bar x_2^TE_2^T - \xi b^T,\; \bar x_1^T
                )
                \\
                &= 
                (
                    E_1^T\bar y + \xi c_1, \;
                    E_2^T \bar y + \xi c_2, \;
                    E_1\bar x_1 + E_2\bar x_2 - \xi b, \;
                    \bar x_1
                )^T. 
            \end{align*}
            \begin{enumerate}
                \item Two multiplications of $E$: $\bar y$ on the left and for $\bar x_1, \bar x_2$ on the right, 
                \item one vector addition with $c = (c_1, c_2)$ and $b$. 
            \end{enumerate}
            Therefore, computing $A^TAv$ has four vector multiplications using $E$. 
            In practice, a sparse matrix $E$ from the model can speed up computations. 
            \par
            Another key operation would be $A^TAv$. 
            Let $\bar v = Av$, then 
            \begin{align*}
                A^TAv &= 
                \begin{bmatrix}
                    E^T_1(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_1
                    \\
                    E^T_2(E_1x_1 + E_2x_2) + (c_1^Tx_1 + c_2^Tx_2 - b^Ty)c_2
                    \\
                    E_1(E_1^Ty + z) + E_2E_2^Ty - (c_1^Tx_1 + c_2^Tx_2 - b^Ty)b
                    \\
                    E_1^Ty + z
                \end{bmatrix}
                \\
                &= 
                \begin{bmatrix}
                    (E_1^TE_1 + c_1^T)x_1 + (E_1^TE_2 + c_2^T)x_2 - (c_1b^T)y
                    \\
                    (E_2^TE_1 + c_1^T)x_1 + (E_2^TE_2 + c_2^T)x_2 - (c_2b^T)y
                    \\
                    -(bc_1^T)x_1 - (bc_2^T)x_2 + (E_2E_2^T + E_1E_1^T + bb^T)y
                    + (E_1E_1^T)z
                    \\
                    E_1^Ty + z
                \end{bmatrix}. 
            \end{align*}
            In practice, implicitly representing the process of $A^TAv$ is better in computing software. 
            Here we write it out to view, for theoretical interests. 
            \par
            Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
            Its gradient, objective value, and Bregman Divergence have: 
            \begin{align*}
                \nabla f(v) &= A^TAv - A^Td, 
                \\
                f(v) &= 
                \frac{1}{2}\langle v, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
                \\
                D_f(x, y) &= \langle x - y, A^TA (x - y)\rangle
                \\
                &= \langle \nabla f(x) - \nabla f(y), x - y\rangle. 
            \end{align*}
            The value $\nabla f(v), f(v)$ when evaluated together, require minimal additional computations. 
            This fact is favorable for implementations in practice. 
            Furthermore, the diference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
            Observe that $\forall u, v \in \RR^n$ it has 
            \begin{align*}
                f(u) - f(v) &= \langle \nabla f(v), u - v \rangle + D_f(u, v)
                \\
                &= \langle \nabla f(v), u - v \rangle + \langle \nabla f(u) - \nabla f(v), u - v\rangle
                \\
                &= \langle \nabla f(u), u - v\rangle. 
            \end{align*}

@@

        % ==============================================================================================================
        % THEOREM | GENERIC GMAPG LS CONVERGENCE IN FXN VAL
        % ==============================================================================================================

@@

@@

        % ==============================================================================================================
        % THEOREM | GENERIC GMAPG LS GRADIENT MAPPING CONVERGENCE
        % ==============================================================================================================
        \begin{theorem}[generic GMAPG LS gradient mapping convergence]

@@

        % ==============================================================================================================
        % EXAMPLE | MFISTA WITH ARMIJO LINE SEARCH
        % ==============================================================================================================

@@

        % ==============================================================================================================
        % EXAMPLE | MFISTA WITH CAMBOLLE'S ADAPTIVE BACKTRACKING
        % ==============================================================================================================
        The following example illustrate Chambolle's adaptive backtracking strategy in the literatures with our GMAPG LS. 

@@

        % ==============================================================================================================
        % EXAMPLE | NESTEROV'S MONOTONE SCHEME WITH GENERIC LINE SEARCH
        % ==============================================================================================================

@@

    \section{Practical enhencements}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section.
